Constant-sized correlations are sufficient to robustly self-test maximally entangled states with unbounded dimension

### 2019-07-26 Draft/draft.tex
new definition of the nonlocal game and tests new formulation of the full test

% Young Tableaux
\usepackage{ytableau}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tM}{\tilde{M}}
\newcommand{\tN}{\tilde{N}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}
\newcommand{\ub}{\underline{b}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\ba}{\pmb{a}}
\newcommand{\bc}{\pmb{c}}
\newcommand{\bS}{\pmb{S}}

@@

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations and mathematical background}
%-----------------------------------
The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we \hf{self-test} is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
\hf{The special form of this maximally entangled state is the effect of our linear system game.} \carl{I don't know what that sentence means.  Refer to something specific.}
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
\hf{the EPR pair is denoted by} 
\begin{align}
	\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are given by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}
\hf{Note that we only work with finite Hilbert spaces in our work.}

@@

We also need some basic notions of group presentation and group
representation, so 
We \hf{introduce them} below.
For more contexts, please refer to Ref.~\cite{dummit2004}.

\hf{
Let $S$ be a set of letters. We denote by $\mathcal{F}(S)$ the \emph{free group generated by $S$}, 
which consists of all finite words made from $\set{s, s^{−1}| s \in S}$ such that no $ss^{−1}$ or $s^{−1}s$ appears as a substring for any $s$,
where $s^{-1}$ denotes the inverse of $s$. 
The group law is given by concatenation and cancellation.
For a more formal treatment, we refer to Section $6.3$ of Ref.~\cite{dummit2004}.}
\carl{This definition is (still) confusing.  It would be ok to simply cite the concept of a free group, provided that you refer to a precise \& complete definition.}

@@

$s_i s_j s_i^{-1} = s_k$ for some $i \neq j$ are called \emph{conjugacy relations}.   \carl{This last sentence
needs to be made more precise (e.g., are
repetitions allows in the linear relations)?}
\hfc{I thought the fact that $\{s_j\}$ is a subset of $S$ guarantees that there will be no repetitions in a linear relation.}

@@

@@

to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and her answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function.

\hf{We also define A nonlocal test 
to be a tuple $(\calX, \calY, \calA, \calB, \pi)$, where
$\calX, \calY, \calA, \calB$ and $\pi$ are as defined for a nonlocal game, so a nonlocal test doesn't have a scoring function.}

A quantum strategy of a nonlocal game presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$. 
By projective measurements, we mean that  
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
\hf{Note that the tensor product structure indicates that the
two parties cannot communicate with each other, which is the reason why such game is called a nonlocal game.}
For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
\calH_B \rightarrow \calH_B$, then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a conditional probability distribution
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.  
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games.
\begin{definition}[Binary linear system game]
 Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ \carl{(meaning that} $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$\carl{)}. 
 The associated linear system game involves two
 players Alice and Bob. 
 Alice is given an equation number $i \in \calX = \{1 \dots m\}$,
 and replies with $\ba \in \calA = \Z_2^{\times n}$.
 Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k=1}^n H(i,k) a(k) \equiv c(i) \pmod 2 \text{ and } a(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
have equations
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
\hf{Note that the equations above are taken modulo $2$.
We follow this convention in the rest of our work.}
For the formulation of a general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.

% \hf{In our work, a binary linear system game is conducted in a slightly different way.
% Instead of always getting an equation number, Alice gets an equation number or 
% a pair of equation number and variable number with equal probability. In the later case,
% she just needs to give assignment to the particular variable.
% By conducting a binary linear system game in this way,
% we force Alice and Bob to share
% a quantum strategy in terms of binary observables.}
% \carl{Is this modification necessary?}
\begin{definition}[Binary observable strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of binary observables for the binary linear system game $Hx = c$ consists of 
\begin{enumerate}
	\item a pair of finite-dimensional Hilbert spaces $\calH_A$ and $\calH_B$; 
	\item a collection of binary observables $N_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $N_j^2 = \1$ for every $1 \leq j \leq n$; 
	\item a collection of binary observables $M_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $M_{ij}^2 = \1$ for every $i,j$, and
		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every \carl{$i,l,k$ such that} $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
\hf{Note that a measurement strategy of a binary linear system game can be converted to a binary observable strategy. Let a  measurement strategy be 
$(\{\{M_i^{\ba}\}_{\ba \in X_i}\}_{i=1}^m, \{\{N_j^b\}_{b=0}^1\}_{j=1}^n,\\ \ket{\psi})$, where $X_i$ is some answer set of equation $i$.
The corresponding binary observable
strategy consists of, $\ket{\psi}$, $N_j := N_j^0 - N_j^1$ and
\begin{align*}
    M_{ij} = \sum_{\ba: a(j)=0} M_i^{\ba} - \sum_{\ba: a(j) =1}
    M_i^{\ba}
\end{align*}
for $1\leq i \leq m$ and $1 \leq j \leq n$. Hence, in the rest of the work, we focus on binary observable strategies.}

@@

The inspiration comes from 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds a group with generators $x$ and $y$ satisfying the relation $xyx^{-1}=y^2$
into the solution group of a binary linear system game.  
We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group
\begin{align}
    \Pg = \ip{u,o:uou^{-1} = o^r},
\label{eq:pgroup}
\end{align}
for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
Since the steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed in the proofs of Proposition~$33$, Lemma~$29$ and
Proposition $27$ of Ref.~\cite{slofstra2017}, 
we defer the formal statements of the embedding procedure till \cref{sec:embedding},
but sketch this procedure in \cref{sec:embed_idea}. 
In \cref{sec:lsg_def}, we define $\Gamma$ and introduce how to
construct $\LS(r)$ from $\Gamma$.
We also highlight a few operators from a finite-dimensional representation of $\Gamma$.
The representation will be used later to build the ideal strategy.

@@

Next, we introduce group $\Pg_1 := \ip{S_1: R_1}$ where $S_0 \subset S_1$, which is a nice conjugacy group defined in \cref{def:nice_conj_grp}.
The special property of $R_1$ is that every relation in $R_0$ can be recovered from $R_1$.
Ensuring that every conjugacy relation is associating two commuting operators is the purpose of introducing $\Pg_1$. 
It makes the construction of a finite-dimension representation of $\Gamma$ from
a finite-dimension representation of $\Pg_1$ easier.
Specifically, in this step, we introduce generators $a_i, b_i, c_i, d_i \in S_1$
for each generator $a_i \in S_0$.
There is also a special generator $f_0 \in S_1$ such that
\begin{align*}
    a_i = b_ic_i = f_0d_i. 
\end{align*}
The relation $a_i = b_ic_i$ guarantees that $b_i$ commutes
with $c_i$.
The generators $b_i$ and $c_i$ are also related by a conjugacy relation
\begin{align*}
    c_i = f_0 b_i f_0. 
\end{align*}
For each $(i,j,k) \in C(r)$, 
$S_1$ contains an auxiliary generator $h_{jk}$, and
$R_1$ 
contains a conjugacy relation 
\begin{align*}
    d_ib_jd_i = c_k,
\end{align*}
and a linear relation
\begin{align*}
    h_{jk}b_jc_k = e.
\end{align*}
The introduction of $h_{jk}$ helps us to deduce that 
$b_j$ commutes with $c_k$.
Hence, every conjugacy relation in $R_1$ is either of the form
$f_0b_if_0 = c_i$ for $1 \leq i \leq r+5$, or
$d_ib_jd_i = c_k$ for $(i,j,k) \in C(r)$.
From the conjugacy relations in $R_1$, it can be proven that
\begin{align*}
    d_ic_jd_i = b_k \text{ for each } (i,j,k) \in C(r).
\end{align*}
Then we can expand $a_ia_ja_i$ by first substituting in $a_i = f_0 d_i$ and $a_j = b_jc_j$ and then repeatedly substituting in the conjugacy relations in $R_1$ and 
the conjugacy relations deduced above, so we can get
\begin{align*}
    a_ia_ja_i = f_0 d_i b_jc_j f_0 d_i
		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
		= (f_0 c_k f_0)(f_0 b_k f_0) 
		= b_k c_k = a_k.
\end{align*}
\carl{It would be good to explain (or at least reiterate) that these relations allow us to recover the conjugacy relations in $\mathcal{R}_0$.}
\hfc{I have added some explanation about the derivation. How does it look?}

@@

A representation of $\Gamma$ can also be built upon
a representation $\Psi_1$ of $\Pg_1$, which is defined on
$\C^2 \x \calH$.
We denote the representation of $\Gamma$ by $\Psi$ and
it is defined on $\C^2 \x \C^2 \x \calH$ such that
\begin{align*}
    \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
    s \in S_1.
\end{align*}
In particular, it means that for each $a_i \in S_0$
\begin{align*}
    \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
\end{align*}
Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
by Lemma $15$ of Ref.~\cite{slofstra2017}.

%----------------------------------------
\subsection{Formal definitions}
\label{sec:gamma_def}
%----------------------------------------
We define the solution group of the linear system game $\LS(r)$ first, which is constructed following the steps
described in the previous subsection.
\begin{definition}
\label{def:gamma}
Define the set $S$ to be 
\begin{align*}
	S = \{J\} \cup \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
\end{align*}
and the set $R$ to be the union of the following
set of linear relations:
\begin{itemize}
\item for each $i = 1 \dots r+5$:
\begin{align*}
	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
	%&g_2 a_i w_i = e \\
	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
\end{align*}
\item for each $ \bc = (i,j,k) \in C(r)$:
\begin{align*}
	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
\end{align*}
\item 
$
	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
$
\item $R_J = \{ JsJs = e \vert s \in S\}$,
\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
\end{itemize}
The group $\Gamma$ is a group with the presentation
$\ip{S:R}$.
\carl{[If you're really going to claim
that this is a complete definition, maybe you should write out the set $C$ somewhere as well?]}
\end{definition}
\hfc{I pointed out in the previous subsection that the definition of $C(r)$ is in the Appendix along with the definition of $\Pg_0$. 
Since $C(r)$ is defined by $\Pg_0$, a stand-alone definition of $C(r)$
will only confuse the reader. Are you suggesting that we don't make this a definition?}

>>>>

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\EXT}{EXT}
\newcommand{\LS}{LS}
\newcommand{\COMM}{COMM}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\tP}{\tilde{P}}
\newcommand{\tQ}{\tilde{Q}}
\newcommand{\tM}{\tilde{M}}
\newcommand{\tN}{\tilde{N}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}
\newcommand{\ub}{\underline{b}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\ba}{\pmb{a}}
\newcommand{\bb}{\pmb{b}}
\newcommand{\bc}{\pmb{c}}
\newcommand{\bS}{\mathrm{S}}

@@

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations and mathematical background}
%-----------------------------------
The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we \hf{self-test} is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
\hf{the EPR pair is denoted by} 
\begin{align}
	\ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are given by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}
Note that we only work with finite Hilbert spaces in our work.

@@

We also need some basic notions of group presentation and group
representation, so 
We introduce them below.
For more contexts, please refer to Ref.~\cite{dummit2004}.

\hf{
Let $S$ be a set of letters. We denote by $\mathcal{F}(S)$ the \emph{free group generated by $S$}, 
which consists of all finite words made from $\set{s, s^{−1}| s \in S}$ such that no $ss^{−1}$ or $s^{−1}s$ appears as a substring for any $s$,
where $s^{-1}$ denotes the inverse of $s$. 
The group law is given by concatenation and cancellation.
For a more formal treatment, we refer to Section $6.3$ of Ref.~\cite{dummit2004}.}

@@

$s_i s_j s_i^{-1} = s_k$ for some $i \neq j$ are called \emph{conjugacy relations}.   

@@

\carl{Nice work with the last two definitions -- they are prettty clean.  I wonder if you could make the last definition even cleaner by simply asserting the relations $s_j s_k = s_k s_j$, and leaving out the generators $s_{jk}$?}
\hfc{If we treat the commutation relations as conjugacy relations, then the final solution will be more complicated.}

@@

to give an answer for a randomly chosen question. 
\hf{We denote Alice's question set by $\calX$ and her family of answer sets by $\{\calA_x\}_x$
for each $x \in \calX$. Similarly,
Bob's question set is denoted by $\calY$ and his family of answer sets denoted by $\{\calB_y\}_y$ for each $y \in \calY$. 
Note that when $\calA_x = \calA$ for each $x \in \calX$, we simply say the output alphabet is $\calA$, and we follow this convention on Bob's side too.
The nonlocal game also
comes with a functions $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and a family of functions $\{ V_{(x,y)} : \calA_x \times \calB_y \rightarrow \R \}_{x,y}$ for each $(x,y) \in \calX \times \calY$, which is 
the family of scoring functions.
Note that when $\calA_x = \calA$ for all $x$ and $\calB_y = \calB$ for all $y$, we write the score function as 
$V: \calA \times \calB \times \calX \times \calY \rightarrow \R$.

\hf{We also define A nonlocal test 
to be a tuple $(\calX, \calY, \{\calA_x\}_{x \in \calX}, \{\calB_y\}_{y \in \calY}, \pi)$, where
$\calX, \calY, \{\calA_x\}_{x}, \{\calB_y\}_{y}$ and $\pi$ are as defined for a nonlocal game.
Hence, a nonlocal test doesn't have scoring functions.
}

A quantum strategy of a nonlocal game or a nonlocal test presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_{a \in \calA_x} \}_{x \in \calX}$ on Alice's side, 
$\{\{N_y^b\}_{b \in \calB_y} \}_{y \in \calY}$ on Bob's side, and a shared state $\ket{\psi}$. 
By projective measurements, we mean that  
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi},
\end{align}
for each $(x,y) \in \calX \times \calY$ and $(a,b) \in \calA_x \times \calB_y$.
Note that the tensor product structure indicates that the
two parties cannot communicate with each other, which is the reason why such game is called a nonlocal game.
For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
\calH_B \rightarrow \calH_B$, then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
\begin{definition}
	Given input alphabets: $\calX$ and $\calY$, and families of output
	alphabets: $\{\calA_x\}_{x \in \calX}$ and $\{\calB_y\}_{y \in \calY}$, a correlation is a family of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA_x, b \in \calB_y\}_{x \in \calX, y \in \calY}$.  
\end{definition}
A particular type of nonlocal games that we are interested in is called binary linear system games.
\begin{definition}[Binary linear system game]
 Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ (meaning that $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$). 
 The associated linear system game involves two
 players Alice and Bob. 
 The input and output alphabets are 
 \begin{align*}
     \calX = \{I_i\}_{i=1}^m && \calY = \{1 \dots n\} \\
     \calA_{I_i} = \Z_2^{|I_i|} && \calB = \Z_2,
 \end{align*}
 where $I_i = \{j : H(i,j) = 1\}$.
 When Alice and Bob answer with $\ba$ and $b$ for questions $I_i$ and
 $j$ respectively,
 the scoring functions are defined by
 \begin{align}
 	V_{(I_i,j)}(\ba, b) =
	\begin{cases}
		1, \quad \text{if } \sum_{k \in I_i} H(i,k) a(k) \equiv c(i) \pmod 2 \text{ and } a(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
\hfc{I think the order of the variables given to Alice doesn't matter, because
the linear system is binary.}
A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
have equations
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
\hf{Note that the equations above are taken modulo $2$.
We follow this convention in the rest of our work.}
For the formulation of a general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.

% \hf{In our work, a binary linear system game is conducted in a slightly different way.
% Instead of always getting an equation number, Alice gets an equation number or 
% a pair of equation number and variable number with equal probability. In the later case,
% she just needs to give assignment to the particular variable.
% By conducting a binary linear system game in this way,
% we force Alice and Bob to share
% a quantum strategy in terms of binary observables.}
% \carl{Is this modification necessary?}
\begin{definition}[Binary observable strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of binary observables for the binary linear system game $Hx = c$ consists of 
\begin{enumerate}
	\item a pair of finite-dimensional Hilbert spaces $\calH_A$ and $\calH_B$; 
	\item a collection of binary observables $N_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $N_j^2 = \1$ for every $1 \leq j \leq n$; 
	\item a collection of binary observables $M_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $M_{ij}^2 = \1$ for every $i,j$, and
		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every \carl{$i,l,k$ such that} $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that a measurement strategy of a binary linear system game can be converted to a binary observable strategy. Let a measurement strategy be 
$(\{\{M_i^{\ba}\}_{\ba \in X_i}\}_{i=1}^m, \{\{N_j^b\}_{b=0}^1\}_{j=1}^n,\\ \ket{\psi})$, where $X_i$ is some answer set of equation $i$.
The corresponding binary observable
strategy consists of, $\ket{\psi}$, $N_j := N_j^0 - N_j^1$ and
\begin{align*}
    M_{ij} := \sum_{\ba: a(j)=0} M_i^{\ba} - \sum_{\ba: a(j) =1}
    M_i^{\ba}
\end{align*}
for $1\leq i \leq m$ and $1 \leq j \leq n$. 
\hf{
Hence, in the rest of the work, we focus on binary observable strategies,
when discussing Alice's strategy of some linear system game.
Specifically, we assume that Alice has a binary observable for each variable
in each equation ,
so when she is asked the assignment of a particular variable, she simply
measures according to the corresponding observable of that variable in some equation.}

@@

The inspiration comes from 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds a group with generators $x$ and $y$ satisfying the relation $xyx^{-1}=y^2$
into the solution group of a binary linear system game.  
We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group
\begin{align}
    \Pg = \ip{u,o:uou^{-1} = o^r},
\label{eq:pgroup}
\end{align}
for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
Since the steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed in the proofs of Proposition~$33$, Lemma~$29$ and
Proposition $27$ of Ref.~\cite{slofstra2017}, 
we defer the formal statements of the embedding procedure till \cref{sec:embedding},
but sketch this procedure in \cref{sec:embed_idea}. 
In \cref{sec:gamma_def}, we define $\Gamma$ and introduce how to
construct $\LS(r)$ from $\Gamma$.
We also highlight a few operators from a finite-dimensional representation of $\Gamma$.
The representation will be used later to build the ideal strategy.

@@

Next, we introduce group $\Pg_1 := \ip{S_1: R_1}$ where $S_0 \subset S_1$, which is a nice conjugacy group defined in \cref{def:nice_conj_grp}.
The special property of $R_1$ is that every relation in $R_0$ can be recovered from $R_1$.
Ensuring that every conjugacy relation is associating two commuting operators is the purpose of introducing $\Pg_1$. \carl{I think a reader would find that last statement unclear.}
\hfc{Maybe we just remove it?}
It makes the construction of a finite-dimension representation of $\Gamma$ from
a finite-dimension representation of $\Pg_1$ easier.
Specifically, in this step, we introduce generators $a_i, b_i, c_i, d_i \in S_1$
for each generator $a_i \in S_0$.
There is also a special generator $f_0 \in S_1$ such that
\begin{align*}
    a_i = b_ic_i = f_0d_i. 
\end{align*}
The relation $a_i = b_ic_i$ guarantees that $b_i$ commutes
with $c_i$.
The generators $b_i$ and $c_i$ are also related by a conjugacy relation
\begin{align*}
    c_i = f_0 b_i f_0. 
\end{align*}
For each $(i,j,k) \in C(r)$, 
$S_1$ contains an auxiliary generator $h_{jk}$, and
$R_1$ 
contains a conjugacy relation 
\begin{align*}
    d_ib_jd_i = c_k,
\end{align*}
and a linear relation
\begin{align*}
    h_{jk}b_jc_k = e.
\end{align*}
The introduction of $h_{jk}$ helps us to deduce that 
$b_j$ commutes with $c_k$.
Hence, every conjugacy relation in $R_1$ is either of the form
$f_0b_if_0 = c_i$ for $1 \leq i \leq r+5$, or
$d_ib_jd_i = c_k$ for $(i,j,k) \in C(r)$.
From the conjugacy relations in $R_1$, it can be proven that
\begin{align*}
    d_ic_jd_i = b_k \text{ for each } (i,j,k) \in C(r).
\end{align*}
Then we can expand $a_ia_ja_i$ by first substituting in $a_i = f_0 d_i$ and $a_j = b_jc_j$ and then repeatedly substituting in the conjugacy relations in $R_1$ and 
the conjugacy relations deduced above, so we can get
\begin{align*}
    a_ia_ja_i = f_0 d_i b_jc_j f_0 d_i
		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
		= (f_0 c_k f_0)(f_0 b_k f_0) 
		= b_k c_k = a_k.
\end{align*}

@@

A representation of $\Gamma$ can also be built from
a representation $\Psi_1$ of $\Pg_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$
that was constructed above. \carl{At this point the reader may be losing track of the precise meaning of what you're saying.  Perhaps you could simply say, ``A representation of $\Gamma$ can also be built from the
representation $\Psi_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$ that was constructed above.''}
\hfc{Fixed, but I worry about the symbol $\circlearrowleft$.}
We denote the representation of $\Gamma$ by $\Psi$ and
it is defined on $\C^2 \x \C^2 \x \calH$ such that
\begin{align*}
    \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
    s \in S_1.
\end{align*}
In particular, it means that for each $a_i \in S_0$
\begin{align*}
    \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
\end{align*}
Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
by Lemma $15$ of Ref.~\cite{slofstra2017}.

%---------------------------------------------------
\subsection{Formal definitions}
\label{sec:gamma_def}
%---------------------------------------------------
We define the solution group of the linear system game $\LS(r)$ first, following the steps described in the previous subsection.
Then we define the game $\LS(r)$.
\begin{definition}
\label{def:gamma}
Define the set $S$ to be 
\begin{align*}
	S = \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
\end{align*}
and the set $R$ to be the union of the following
set of linear relations:
\begin{itemize}
\item for each $i = 1 \dots r+5$:
\begin{align*}
	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
	%&g_2 a_i w_i = e \\
	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
\end{align*}
\item for each $ \bc = (i,j,k) \in C(r)$:
\begin{align*}
	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
\end{align*}
\item 
$
	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
$
\item $R_J = \{ J s J s = e \vert s \in S\}$,
\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
\end{itemize}
\hf{The group $\Gamma$ is a group with the presentation
$\ip{S \cup \{J\} : R}$.}
\end{definition}
